
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Image morphology}
\label{sec:morph}

The main input of a modeller to the process is a markup of the
candidate lens system, which we call a spaghetti diagram.  This is a
sketch of the arrival-time surface from a point-like source, with
proposed locations of maxima, minima and saddle points, and an implied
time-ordering of the images.  Such information encodes a starting
proposal for the mass distribution.  A spaghetti diagram is thus a
completely abstract construction, and moreover it refers to a
simplified system with a point source.  However, spaghetti diagrams
are intuitive because they tend to resemble the form of lensed arcs
\citep[see fig.3 of][]{2008MNRAS.383..857F}, and of course they are
simple to draw, and easy to vary and refine in an open collaborative
environment. This makes them very practical for non-professional lens
enthusiasts in the citizen-science community.  Details and tests are
given in \citet{2015MNRAS.447.2170K}.

We now discuss the diagnostics that can be taken from the process of
drawing the spaghetti diagram, even before detailed mass-modelling
takes place.  Fig.~\ref{fig:splinput} shows nine examples, each
consisting of a cutout of the \SW  image of a lens candidate,
marked up with a spaghetti diagram.
The volunteers are initially presented a square image with side
82\arcsec (440~pixels) in full size, but they have the
ability to zoom in individually.
The cutouts presented in Figs.~\ref{fig:splinput} to \ref{fig:kappa}
are rescaled during post-processing, relative to the outermost image.
% it's a factor L/(L-4) with L=pixradius, for L=12 -> 1.5
% maprad = rmax * L / (L-4)

All the examples shown in Fig.~\ref{fig:splinput} identify five locations:
the centre of the main lensing galaxy, which is also a maximum of the
arrival time surface (red dots); two minima (blue dots); and two
saddle points (green dots and also self-intersections of the curves).
Only two (\sw{05} and \sw{42}) of the nine systems, however, have five
distinct features in plausible locations.  In the other seven
examples, an arc is interpreted as a blend of three or four images.
This defines the `unblended images' diagnostic.  Note that this
characterisation could be different if the spaghetti diagram were 
different.  For example, \sw{28} has also been modelled with the arc on
the right interpreted as a single image, rather than as three images
as shown in the figure; for such a model, the `unblended images'
diagnostic would be true.

The second diagnostic checks whether all images are visible.  For example,
we see in \sw{58} at the top left of Fig.~\ref{fig:splinput} that an
image at the second minimum is conjectural and does not correspond to
any visible feature.

The third diagnostic tests whether the lens is isolated, or whether
other galaxies could contribute to the lensing.  For this, we do not
consider stars or other clearly foregound objects.  Additional
galaxies contributing to the lensing mass can be marked by the
volunteer alongside the spaghetti diagrams.  An example can be seen as
the grey dot and circle in the cutout with \sw{57} at the top right of
Fig.~\ref{fig:splinput}.  Objects marked in this way are modelled as
point masses.  Other possible contributors to lensing are galaxies or
groups that are not in the immediate vicinity of the lensed images,
yet massive enough to exert an influence. These are accounted for by
allowing a constant but adjustable external shear.

We remark that the lack of expected lensed images, or the presence of
blended images or perturbing galaxies do not imply that a given
candidate is unlikely to be a lens.  This means, rather, that the
models are more uncertain and perhaps could be more easily improved by
trying further variations in the markup.

The fourth diagnostic is based on the fact that the arrangement of
lensed images of a pointlike source through a non-circular
gravitational lens depends on the location of the source relative to
the long and short axes of the lens.  This dependence is quite robust
and independent of many other details of the lensing mass
distribution.  Sources close to being dead-centre behind a lens tend
to produce quads; sources at larger transverse distance tend to
produce doubles.  We denote these as Q and D, respectively, and add a
prefix to the Q systems, as follows: we write LQ if the source is
inferred as displaced along the long axis of the lens, SQ if displaced
along the short axis, IQ if inclined to both axes, CQ if only very little or
no displacement is evident.  Although the
unlensed source and its location are obviously not seen, the LQ, SQ, IQ and CQ
cases correspond to easily-seen image morphologies \citep[see,
  e.g.,][]{2003AJ....125.2769S}.
\begin{itemize}
\item The simplest is the SQ case: this creates a saddle point and two
  minima in an arc, with the second saddle point on the other side of
  the lensing galaxy, at a closer to the galaxy than the arc.  \sw{58}
  and \sw{28} in the upper row of Fig.~\ref{fig:splinput} are typical
  examples of SQ.  If the source were moved outwards along the short
  axis, the minimum-saddle-minimum set would merge into a single minimum,
  leaving a D system; the transition is known as a cusp catastrophe.
\item The middle row of Fig.~\ref{fig:splinput} shows three IQ
  systems: \sw{05}, \sw{42} and \sw{19}.  This type has a characteristic
  asymmetry, often with two images close together.  If the source
  were moved outwards, the minimum-saddle pair would merge and
  mutually cancel, leaving again a D system. This transition is known
  as a fold catastrophe.
\item The lower row of Fig.~\ref{fig:splinput} shows three LQ
  systems: \sw{09}, \sw{29} and \sw{02}. The failed model, \sw{57}, at top right
  may also belong to this category.  Here the images have a
  fairly symmetric arrangement with an arc and a counter-image on the
  other side, but the spaghetti diagram is completely asymmetric.  If
  the source were moved outwards along the long axis, the
  saddle-minimum-saddle set  would merge into a single saddle --- another
  form of cusp catastrophe.  LQ can be visually distinguished from SQ
  by the relative distances of the arc and the counter-image.  For
  LQ the arc is closer, for SQ the counter-image is closer.
\end{itemize}
CQ systems are often called `cross' or `Einstein-cross' systems; IQ
systems are sometimes called `folds', with `cusp' commonly used for
both SQ and LQ.  The labels `short-axis quad' and so on are not
standard in the literature, but the morphological classification they
express is familiar to experienced modellers.  Hence they can be
useful to researchers wishing to apply other modelling methods to the
same systems.

