\section{SpaghettiLens}\label{sec:spl}

SpaghettiLens is an example of a medium-sized collaboration spawned by
a large citizen-science project (in this case Space~Warps).  While
collaboration with volunteers is essential to both, the form of
collaboration is very different.  In Space~Warps, volunteers in a
crowd of $\gtrsim10^4$ make independent contributions.  Each person is
presented with a random selection of survey-patches and invited to (in
effect) vote on each.  The system estimates each volunteer's skill
level according to test-patches interspersed with the real data, and
weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
an active forum for volunteers, but since everyone is seeing different
data samples with minimal overlap, the forum has little if any
influence on votes.  With SpaghettiLens, on the other hand, there is a
small group of volunteers and their contributions are interdependent.

A modeller's main input to SpaghettiLens is a sketch of arrival-time
contours on a lensed system.  It gives the locations (or best-guess
locations) of images of point-like sources, along with their ordering
in arrival time, and their parities (minumum, saddle-point or
maximum).  Such a sketch, which we call a spaghetti diagram, tends to
resemble the form of lensed arcs, but it also in effect 
encodes a proposal for its mass distribution.  A spaghetti diagram is
read by a server-side numerical engine \citep[GLASS, developed
  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
of mass maps.  The mass maps are made up of mass tiles and are
free-form, except that they are required to be concentrated around the
identified lens centre.  They are also required to reproduce the given
image locations, parities and time ordering exactly.  Graphical
representations of the mass map and arrival-time surface are returned
to the user for review.  The user can post these results on a forum,
or discard them and try again.  Volunteers can start the modelling
process afresh, or they can take an existing model from the forum and
modify its input spaghetti diagram or its accompanying options, and
thus obtain a revised model.

